Figures

### 2019-05-22 figures/01_county_extent.Rmd
embiggen map
plot residual spatial autocorrellation range

```{r tptn_maps, echo=FALSE}
ep         <- readRDS("../data/ep.rds")

@@

>>>>

```{r tptn_maps, echo=FALSE, fig.width=7}
ep         <- readRDS("../data/ep.rds")

@@

```{r }
# residual autocorrelation range
pnt <- LAGOSNE::coordinatize(ep[1,])

ggplot() + 
  geom_sf(data = state_intersects) +
  geom_sf(data = st_buffer(pnt, 0.3), color = "red") +
  geom_sf(data = pnt, size = 0.5) +
  coord_sf(datum = NA) +
  plot_opts
```
